# Welcome to Mia's Assignment B1!

Welcome to the code for my assignment! Throughout the following code, I will create, document, demonstrate, and test a function. Follow along to see the process.

------------------------------------------------------------------------

## Setup

Here, I will make sure I have all appropriate libraries loaded in.

```{r libraries}

library(tidyverse)
library(dplyr)
library(testthat)
library(devtools)
library(palmerpenguins)

```

If you don't have the above packages installed, you can use the code chunk below to install them.

```{r install}

```

------------------------------------------------------------------------

## Exercise 1 & 2: Make and Document a Function

Here, I will make my function. I will also document it, so that it is easy to understand what I have done and why.

First, I will outline the purpose of my function. When working with datasets, I often wish to produce multiple summary statistics for some variable or other. Writing out the code for these summary stats, especially if I wish to see them for multiple variables, can be quite tiresome. So here, I will create a function that will produce a table of the desired summary statistics for the variables I enter. These summary statistics will be the: mean, range, minimum, first quartile, median, third quartile, and maximum.

```{r new function}

#' #Summary Statistics for a Numeric Variable 
#' 
#' @description
#' Creates a table of summary statistics for a variable. These summary statistics are the mean, range, minimum, first quartile, medan, third quartile, and maximum of the variable.
#' 
#' @param data The name of the dataset being pulled from. Named data so that it's purpose is clear.
#' @param ... The variable(s) used to group the data. Ellipses are used because the user may or may not want to group their data, or they may wish to group by one or multiple variables.
#' @param summ_var The variable(s) for which the summary statistics will be generated. Named summ_var to be clear that this is the variable for which a summary will be generated.
#' 
#' @return A new data frame. Each column is one summary statistic. Each row is  for a combination of grouping variables.

total_summary <- function(data, ..., summ_var, na.rm = FALSE) {
  if(!is.numeric(data[[deparse(substitute(summ_var))]])) {
    stop("Sorry, this function only works for numeric variables. It seems the variable you inputted is of class:", class({{summ_var}}))
  }
  data %>%
    group_by(...) %>%
    summarize(mean = mean({{summ_var}}, na.rm = na.rm),
            range = max({{summ_var}}, na.rm = na.rm) - min({{summ_var}}, na.rm = na.rm),
            min = min({{summ_var}}, na.rm = na.rm),
            first_quartile = quantile({{summ_var}}, 0.25, na.rm = na.rm),
            median = median({{summ_var}}, na.rm = na.rm),
            third_quartile = quantile({{summ_var}}, 0.75, na.rm = na.rm),
            max = max({{summ_var}}, na.rm = na.rm))
}

```

------------------------------------------------------------------------

## Exercise 3: Include Examples

Here, I will show some example of my function, *total_summary*, functioning. I will use the data from the *penguins* dataset that I loaded in the **Setup** section, though any dataset should work.

First, let's take a look at the *penguins* dataset.

```{r penguins}

print(penguins)
glimpse(penguins)

```

Now I will use this data to show the use of my function.

```{r example 1}

total_summary(penguins, species, summ_var = body_mass_g, na.rm = TRUE)

```


------------------------------------------------------------------------

## Exercise 4: Test the Function

Here, I will...

```{r}

```
