# Welcome to Mia's Assignment B1!

Welcome to the code for my assignment! Throughout the following code, I will create, document, demonstrate, and test a function. Follow along to see the process.

------------------------------------------------------------------------

## Setup

Here, I will make sure I have all appropriate libraries loaded in.

```{r libraries}

library(tidyverse)
library(dplyr)
library(testthat)

```

If you don't have the above packages installed, you can use the code chunk below to install them.

```{r install}

```

------------------------------------------------------------------------

## Exercise 1 & 2: Make and Document a Function

Here, I will make my function. I will also document it, so that it is easy to understand what I have done and why.

First, I will outline the purpose of my function. When working with datasets, I often wish to produce some summary statistics for some variable or other. Writing out the code for these summary stats, especially if I wish to see them for multiple variables, can be quite tiresome. So here, I will create a function that will produce a table of the desired summary statistics for the variables I enter.

```{r new function}

# Desired stats to be known / format of function

#  summarize(mean = mean(numeric_var),
#            range = max(numeric_var) - min(numeric_var),
#            min = min(numeric_var),
#            1st_quartile = quantile(numeric_var, 0.25),
#            median = median(numeric_var)
#            3rd_quartile = quantile(numeric_var, 0.75)
#            max = max(numeric_var)),

#glimpse(summ_diff_area)

total_summary <- function(data, ..., summ_var) {
  if(!is.numeric(summ_var)) {
    stop("Sorry, this function only works for numeric variables. It seems the variable you inputted is ", class(summ_var))
  }
  data %>%
    group_by(...) %>%
    summarize(mean = mean(summ_var),
            range = max(summ_var) - min(summ_var),
            min = min(summ_var),
            first_quartile = quantile(summ_var, 0.25),
            median = median(summ_var),
            third_quartile = quantile(summ_var, 0.75),
            max = max(summ_var))
}


```

